CRUSE to Safe Cycling in Ireland

### 2023-09-29 paper.qmd
Plurality fix
Comment-out random study bit

A proactive approach to the development of cycling policy and infrastructure is taking place in Ireland.
The main framework underpinning these efforts is the Climate Action Plan[^2] and The National Development Plan[^3].
Strategic alignment is also outlined by the Phoenix Park Transport and Mobility Options Study, which highlights public support for active travel interventions: while only 3% of trips in Ireland are made by cycling according to the latest Census data from 2016,^[
https://assets.gov.ie/42950/f789b2fcfb144441822f58236986eeea.pdf
] "83% of respondents supported enhanced walking and cycling facilities".

>>>>

A proactive approach to the development of cycling policy and infrastructure is taking place in Ireland.
The main frameworks underpinning these efforts are the Climate Action Plan[^2], the National Development Plan[^3], and the National Roads 2040 strategy^[
https://www.tii.ie/tii-library/strategic-planning/national-roads-2040/TII-NR2040-Final-Report-EN-April-2023.pdf
].
<!-- Strategic alignment is also outlined by the Phoenix Park Transport and Mobility Options Study, which highlights public support for active travel interventions: while only 3% of trips in Ireland are made by cycling according to the latest Census data from 2016,^[ -->
These policy frameworks are backed-up by public support for active travel interventions: while only 3% of trips in Ireland are made by cycling according to the latest Census data from 2016,^[
https://assets.gov.ie/42950/f789b2fcfb144441822f58236986eeea.pdf
] "83% of respondents supported enhanced walking and cycling facilities".
